%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Extracurricular Activities}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------
\begin{cventries}
    \cventry
    {\textbf{Chairperson, Bible Study Leader}} % Affiliation/role
    {InterVarsity Christian Fellowship (IVCF)} % Organization/group
    {Singapore} % Location
    {2021 - 2023} % Date(s)
    { % Description(s) of experience/contributions/knowledge
        \begin{cvitems}
            \item {Chairperson of IVCF. Involved in leading the chapter, supervising executive team, and organizing events.}
            \item {Small Group Bible Study Leader. Involved in leading a study session of the Bible and mentoring students under my care both spiritually and emotionally.}
        \end{cvitems}
    }
\end{cventries}

\begin{cventries}
    \cventry
    {\textbf{Philly Missions Leader}} % Affiliation/role
    {Inter-Fellowship Association (IFA)} % Organization/group
    {Singapore} % Location
    {Mar 2023} % Date(s)
    { % Description(s) of experience/contributions/knowledge
        \begin{cvitems}
            \item {Co-led a week-long missions trip to Kensington, Philedalphia, where we helped various long-term ministires that tended to the homeless and drug addicted population there. The team gave out food, played music, prayed with them, and talked to them about Jesus. We also hosted a Vacation Bible School session for the kids.}
            \item {Involved with coordinating trip logistics, communicating with various ministries, and overseeing and mentoring the 19-person team.}
        \end{cvitems}
    }
\end{cventries}

\begin{cventries}
	
	%------------------------------------------------
	
	\cventry
	{\textbf{Chairperson}} % Affiliation/role
	{CMU Foosball Club} % Organization/group
	{Singapore} % Location
	{2020 - 2023} % Date(s)
	{ % Description(s) of experience/contributions/knowledge
		\begin{cvitems}
			\item {Chairperson of the CMU Foosball Club. Revived the club after 6 years of inactivity.}
%			\item {Intending to participate in next year's Kentucy foosball state championships.}
		\end{cvitems}
	}
\end{cventries}

\begin{cventries}

%------------------------------------------------

\cventry
{\textbf{Chairperson}} % Affiliation/role
{Hwa Chong Computer and Robotics Club} % Organization/group
{Singapore} % Location
{2011 - 2016} % Date(s)
{ % Description(s) of experience/contributions/knowledge
\begin{cvitems}
	\item {Chairperson of the Junior College (2016) and High School (2014) section of the club. \newline
		Facilitated the merger and co-operation of the computer and robotics club.}
	\item {Gained expertise in web and game programming through self-motivated learning. \newline
		Also trained for the National Informatics Olympiad, and attained bronze in 2013.}
	\item {Challenged my programming skills by participating in several team competitions:}
\end{cvitems}
}
\end{cventries}

\begin{cvhonors}
	%------------------------------------------------
	
	\cvhonor
	{3rd} % Award
	{NYAA Canada-Singapore Website Design Competition} % Event
	{} % Location
	{2015} % Date(s)
	
	%------------------------------------------------
	
	\cvhonor
	{Consolation Award (4th)} % Award
	{Singapore Games Creation Competition \textit{(SGCC)} \infoButton{https://samleo8.github.io/games/playFlash.html?name=DruggedDreams}} % Event
	{} % Location
	{2015} % Date(s)	
	
	%------------------------------------------------
	
	\cvhonor
	{Finalist (Top 5)} % Award
	{Splash Awards \textit{(app prototyping competition)}} % Event
	{} % Location
	{2014} % Date(s)	
	
	%------------------------------------------------
	
	\cvhonor
	{Commendation Award (Top 10)} % Award
	{SGCC \infoButton{https://samleo8.github.io/games/playFlash.html?name=Nostalgia}} % Event
	{} % Location
	{2014} % Date(s)	
	
	%------------------------------------------------	
\end{cvhonors}

\iffalse
\begin{cventries}
	
	\cventry
	{\textbf{Participant}} % Affiliation/role
	{Young Defense Scientist Programme (YDSP)} % Organization/group
	{Singapore} % Location
	{2011 - 2016} % Date(s)
	{ % Description(s) of experience/contributions/knowledge
		\begin{cvitems}
			\item { Participant of the Young Defense Scientist Programme organised by Singapore's Defense and Technological Agency (DSTA) and DSO National Laboratories: }
		\end{cvitems}
	}
\end{cventries}

\begin{cvhonors}
	\cvhonor
	{SSEF Gold, ISEF Delegate} % Award
	{Research@YDSP (\fancyref{lightDirectionFinderProject}{Light Direction Finder})} % Event
	{} % Location
	{2015} % Date(s)	
	
	\cvhonor
	{Participant} % Award
	{World of Science Workshop (Signal Processing)} % Event
	{} % Location
	{2015} % Date(s)
	
	\cvhonor
	{Participant} % Award
	{Research@YDSP (\fancyref{eyeTrackingProject}{Analysis of Multimodal Interaction Methods})} % Event
	{} % Location
	{2014} % Date(s)
	
	\cvhonor
	{Participant} % Award
	{World of Science Workshop (Computer Security)} % Event
	{} % Location
	{2014} % Date(s)
	
	\cvhonor
	{Participant} % Award
	{World of Science Workshop (Artificial Intelligence)} % Event
	{} % Location
	{2014} % Date(s)
\end{cvhonors}
\fi